\section{Motivation}
\label{motiv:sec}

\subsection{Motivating Examples}
\label{examples:sec}

\input{example1.tex}

Let us use a few real-world examples to explain the problem and
motivate our approach. Figure~\ref{fig:example1} displays a code
snippet in an answer to the StackOverflow (S/O) question 15409223 on how to
``add new paths for native libraries at runtime in Java''.  The code
snippet serves as an illustration in the S/O post, thus, does
not contain all the details on what exceptions that need to be
handled. It contains only a throw of a generic \code{Exception} in the
method header~(\code{addLibraryPath}). From the empirical study from
Zhang {\em et al.}~\cite{zhang-icse19}, this code snippet was adopted
by the developers into their Github project named \code{armint} (see
Figure~\ref{fig:example2}). In \code{armint} code, the developers
handle in a \code{try-catch} block all possible exceptions caused by
\code{java\-.lang\-.Class\-.get\-Declared\-Field(...)} (line 7)
according to JDK's documentation including
\code{No\-Such\-Field\-Exception}, \code{Security\-Exception},
\code{Illegal\-Argument\-Excep\-tion}, and
\code{Illegal\-Access\-Exception} (line 24 of
Figure~\ref{fig:example2}).

%In their study, Zhang {\em et al.}~\cite{zhang-icse19} have reported
%that
%Such adaptation is still largely manual~\cite{zhang-icse19}.
%Kechagia {\em et al.}~\cite{kechagia-msr14} found that 69\% of the
%methods from Android packages in their stack traces had undocumented
%exceptions in the Android APIs.
The manual adaptation on exception handling by inserting a
\code{try-catch} block is quite popular, yet not automated by any
tools~\cite{zhang-icse19}. Such manual adaptation for a code snippet
could lead to exception-related bugs, which could cause serious issues
including crashes or unstable states. It is not trivial for developers
to memorize what API methods could cause exceptions and what
exceptions need to be handled~\cite{xrank-fse20}. Thus, it is
desirable to have an automated tool to recommend proper exception
handling in order to adapt the incomplete code snippets.  Such a tool
could recommend if a \code{try-catch} block is needed for the snippet,
what lines need to be included in that block, and what exception types need
to be handled.


\begin{Observation} [{\bf Exception Handling Recommendation}]
\label{ob1}
Automated recommendation to handle exceptions is desirable to
assist developers in adapting incomplete code snippets into their
codebases.
\end{Observation}

%spec, heuristic, mining, IR

As explained in Section~\ref{sec:intro},  four
categories of automated approaches have been proposed to recommend
exception
handling~\cite{xrank-fse20,barbosa-bsse12,chanchal-scam14,barbosa-tse18,barbosa-tse16}. While
early approaches were not effective in all cases due to their {\em
  heuristics}~\cite{barbosa-bsse12}, the {\em exception policies} are
too strict in enforcing them, yet requires the rules to be encoded in
the tools~\cite{barbosa-tse16,barbosa-saner18}. The state-of-the-art
{\em information retrieval}-based approaches (e.g.,
XRank/Xhand~\cite{xrank-fse20}) have been shown to outperform the
existing approaches including the {\em mining
  approaches}~\cite{chanchal-scam14} (which suffers the issue of setting a
threshold for frequent occurrences).

%XRank~\cite{xrank-fse20} and XHand~\cite{xrank-fse20} have shown that
%information retrieval (IR) techniques such as fuzzy sets could perform
%better than the mining approaches~\cite{chanchal-scam14}, which
%suffers the issue of setting a threshold for frequent occurrences.

However, the state-of-the-art, IR-based approaches~\cite{xrank-fse20}
have the following key limitations. First, it is not trivial to
pre-define a threshold for feature matching for a retrieval, e.g., the
threshold to determine the associations between an API~call (e.g.,
\code{get\-Declared\-Field}) and an exception type (e.g.,
\code{No\-Such\-Field\-Exception}). Second, relying on the lexical
values of the elements' names, XRank/XHand~\cite{xrank-fse20} cannot
handle the ambiguous names of the APIs or exceptions (e.g., the API
method \code{get} at line 6 of Figure~\ref{fig:example1} occurs in
multiple libraries) in an incomplete code snippet, which might be
unparseable for fully-qualified name resolution. Thus, this reduces
its effectiveness. Finally, XRank/XHand~\cite{xrank-fse20} consider
only the associations between an API method with an exception type,
and discard the surrounding code context in a \code{try-catch} block.
For example, they compute the association between the names of
the API call (e.g., \code{get\-Declared\-Field}) and the exceptions
(e.g., \code{No\-Such\-Field\-Exception}, \code{Security\-Exception},
etc.)  that need to be handled. Without the context, it is even more
challenging to decide the identities of the APIs via only simple
names.

%This makes their tool further suffer the ambiguity issue.


%Earlier approaches utilized {\em heuristic strategies} on exception
%types, method calls, and variables' types to recommend exception
%handling code~\cite{barbosa-bsse12}. While the heuristics might not
%work in all the cases, other approaches enforce {\em exception
%  handling policies}~\cite{barbosa-tse16,barbosa-saner18}. However,
%the policies must be pre-defined and encoded in the tool. To overcome
%that, the {\em mining approaches} are based on the idea that similar
%code requires similar exception handling~\cite{chanchal-scam14}.
%Some approaches also leverage mined patterns to repair
%exception-handling bugs~\cite{zhong-jss18}.
%A key issue with the mining approaches is that the two code fragments
%might not be exactly matched, but they share a few key elements that
%require the same exception handling.  Thus, Nguyen {\em et
%  al.}~\cite{xrank-fse20} propose an {\em information retrieval} (IR)
%approach using a fuzzy set technique to learn the associations between
%the method calls (e.g., \code{get\-Declared\-Field}) and the
%exceptions (e.g., \code{No\-Such\-Field\-Exception},
%\code{Security\-Exception}, etc.)  that need to be handled. A key
%drawback of the IR approach is that it relies on the threshold for a
%match in an retrieval, which might often not be easily pre-defined.


%To address the issue, several automated approaches have been proposed
%to recommend proper exception
%handling~\cite{xrank-fse20,barbosa-bsse12,chanchal-scam14,barbosa-tse18,barbosa-tse16}. Earlier approaches utilized {\em heuristic strategies} on exception types, method calls, and variables' types to recommend exception handling
%code~\cite{barbosa-bsse12}. While the heuristics might not work in all
%the cases, other approaches enforce {\em exception handling
%  policies}~\cite{barbosa-tse16,barbosa-saner18}. However, the
%policies must be pre-defined and encoded in the tool. To overcome
%that, the {\em mining approaches} are based on the idea that similar
%code requires similar exception handling~\cite{chanchal-scam14}.
%A key issue with the mining approaches is that the two code fragments
%might not be exactly matched, but they share a few key elements that
%require the same exception handling.  Thus, Nguyen {\em et
%  al.}~\cite{xrank-fse20} propose an {\em information retrieval} (IR)
%approach using a fuzzy set technique to learn the associations between
%the method calls (e.g., \code{get\-Declared\-Field}) and the
%exceptions (e.g., \code{No\-Such\-Field\-Exception},
%\code{Security\-Exception}, etc.)  that need to be handled. A key
%drawback of the IR approach is that it relies on the threshold for a
%match in an retrieval, which might often not be easily pre-defined.

\input{example2.tex}

%\subsection{Observations}
%\label{sec:obs}

%To facilitate the reuse of code snippets in a forum, an automated tool
%is needed to derive the fully-qualified names of the API elements in
%the snippets so that the proper import statements are added in the
%code.
%To build an automated tool to assist developers in proper exception
%handling, we draw the motivation from the following observations.

\input{example3.tex}

Now, consider the complete code example in Figure~\ref{fig:example3}
from the Github project named \code{quarkus}. While there are
differences between the complete code in Figure~\ref{fig:example3} and
the adapted code in Figure~\ref{fig:example2}, due to the presence of
the API call to \code{get\-Declared\-Field} in both code, the list of
the handled exceptions is the same (line 8 in
Figure~\ref{fig:example3} and line 24 in
Figure~\ref{fig:example2}). This is expected because the designers of
the JDK library have the intent for developers to use the API method
\code{get\-Declared\-Field} within a \code{try-catch} block and to
handle the list of exceptions as in line 8 of
Figure~\ref{fig:example3}. Thus, to adapt the incomplete code snippet
in Figure~\ref{fig:example1}, one could learn from the public code
repositories to properly handle the exceptions.

\begin{Observation} [{\bf Regularity of Exception Handling}]
\label{ob2}
Finding the patterns from complete code in existing code corpora could
be a good strategy to {\bf learn to properly handle the exceptions} in
adapting an (incomplete) code snippet into a codebase.
\end{Observation}

%Tien
%Explain on using context to determine the APIs and exception types
%And make connections between them.

%=======================================================
\begin{Observation} [{\bf Connections between API methods and Exceptions}]
\label{ob3}
The presence of certain API elements helps decide the exceptions that
need to be handled.
\end{Observation}

In our motivating example, the connection between
\code{java.\-lang.\-Class.\-get\-Declared\-Field} and the exceptions
\code{No\-Such\-Field\-Exception}, \code{Secur\-ity\-Exception},
\code{Illegal\-Argument\-Exception}, and
\code{Illegal\-Access\-Exception} can be learned from the existing
code corpora. Thus, a model can learn to recommend those exceptions
for an incomplete code snippet involving \code{get\-Declared\-Field}.
%======================================================

\begin{Observation} [{\bf Dependencies and Surrounding Context Help Resolve Name Ambiguity}]
\label{ob4}
The program dependencies among the API elements and the surrounding
code context can help resolve the ambiguity of the names of those
elements in incomplete code snippets.
\end{Observation}

For an incomplete code snippet, as explained earlier, the simple names
of the API elements (methods, fields, classes) could be ambiguous.
However, if a model can learn from the complete code the
fully-qualified names (FQNs) of the API elements, the context
consisting of those API elements and their program dependencies
%as well as the other program elements in the surrounding context
could help a model determine the correct identities of the API
elements, leading to correct prediction of the handled exceptions.
%
In Figure~\ref{fig:example1}, to determine the identities of
\code{Field} (line 2), \code{get\-Declared\-Field} (line 2),
\code{set\-Accessible} (line 3), \code{get} (line 6), etc., a model
could rely on the dependencies among them in the surrounding context.
For example, the return type of \code{get\-Declared\-Field} is
\code{Field} (thanks to line 2), which has an API method named
\code{set\-Accessible} (thanks to line 3) and another API method named
\code{get} (thanks to line 6). Considering all such dependencies among
the API elements in the context and with the knowledge learned from
the complete code, a model could decide that the identity of
\code{Field} is \code{java.\-lang.\-Class.\-Field}, that of
\code{set\-Accessible} is
\code{java.\-lang.\-Class.\-Field.\-set\-Accessible}, and that of the
\code{get} function at line 6 is
\code{java.\-lang.\-Class.\-Field.\-get}. The rationale is that a
model could see such dependencies among those API elements before in
a complete code in the training corpus.

%that of \code{Field} is
%\code{java.\-lang.\-Class.\-Field}, and that of \code{set\-Accessible}
%is \code{java.\-lang.\-Class.\-Field.\-set\-Accessible}.


%======================================================
For the list of statements in an incomplete code, not all of them
needs to be wrapped around in a \code{try-catch} block. For example,
considering the example of using \code{new\-Buffered\-Reader} in
Figure~\ref{fig:example4}. While the API call
\code{java.\-nio.\-file.\-new\-Bugffered\-Reader} needs to be within a
\code{try-catch} block, the statement at line 1 to retrieve the
character set does not. Moreover, the statement at line 5 with the API
call to \code{readLine} needs to be wrapped in a \code{try-catch}
block as well.

\input{example4.tex}

\begin{Observation} [{\bf Learn to Decide What Statements to be in a Try-Catch block}]
\label{ob5}
  A model can learn from the code corpora what statements need to be placed
  within a \code{try-catch} block or not.
\end{Observation}
